Demystifying the Computer Science PhD Admission in the US\\{\large A Guide for International Students

### 2024-01-05 demystify.tex
updates

\paragraph{Shared Spreadsheet} Many students use a spreadsheet to help them and their letter writers to keep track of their applications. They often use a shared spreadsheet (e.g., using Google Docs or Sheets).  Here are some information to put on the sheet.  
\begin{itemize}
\item \textbf{Your info}: Full name, email, phone, link to website/CV).  This is helpful for the writers just in case they want to quickly get some information about you.
\item \textbf{Applications details}: University, Dept, Application System URL, Submission Deadlines, Application Status (e.g., submitted,  rejected, wait-listed, accepted)
\item \textbf{LoRs}: Writer 1, Writer 2, Writer 3.  If this is a shared document, you might want to omit names and just use writer X. Under each is their status, e.g., sent/not yet/reminder needed, etc.

>>>>

\paragraph{Shared Spreadsheet} Many students use a (shared) spreadsheet, e.g., Google Sheets/Docs, to help them and their letter writers to keep track of their applications. Here are some information to put on the sheet.
\begin{itemize}
  \item \textbf{Your info}: Full name, email, phone, link to website/CV.  This is helpful for the writers just in case they want to quickly get some information about you.

  \item \textbf{Applications details}: University, Dept, Application System URL, Submission Deadlines, Application Status (e.g., submitted,  rejected, wait-listed, accepted)

  \item \textbf{LoRs}: Writer 1, Writer 2, Writer 3.  If this is a shared document, you might want to omit names and just use writer X. Under each is their status, e.g., sent/not yet/reminder needed, etc.
